The Project aim to scrap web data from the Nigeria Center for Disease Control NCDC
To help analyse COVID19 cases in Nigeria. Data was scrapped from https://covid19.ncdc.gov.ng/ on the 11/14/2020 at 2:55am.


```{r}
library(rvest)
library(dplyr)
link="https://covid19.ncdc.gov.ng/#!"
page = read_html(link)
Naija_Covid_data= page %>%html_table(fill = T)
Naija_Covid_data
length(Naija_Covid_data)
summary(Naija_Covid_data)
typeof(Naija_Covid_data)
write.table(Naija_Covid_data, file = "Naijacovid_data_13_11_20.csv", sep = ",")
```

I Need to covert the data from List to a dataframe
```{r}
Naijacovid<-data.frame(Naija_Covid_data)
head(Naijacovid)
```
I want to rename the column names
```{r}
colnames(Naijacovid)
colnames(Naijacovid)<-c("States_Affected", "Confirmed_Cases", "Cases_On_Admission", "Discharged_cases", "No_of_Deaths")
colnames(Naijacovid)
```

I want to get rid of the commas in the numbers using the Gsub function

```{r}
Naijacovid$Confirmed_Cases<-gsub(",", "", Naijacovid$Confirmed_Cases)
Naijacovid$Cases_On_Admission<-gsub(",", "", Naijacovid$Cases_On_Admission)
Naijacovid$Discharged_cases<-gsub(",", "", Naijacovid$Discharged_cases)
head(Naijacovid)
```
checking for the data str
```{r}
str(Naija_Covid_data)
```
coverting character column 2,3,4 to intergers

```{r}
Naijacovid$Confirmed_Cases<-as.integer(Naijacovid$Confirmed_Cases)
Naijacovid$Cases_On_Admission<-as.integer(Naijacovid$Cases_On_Admission)
Naijacovid$Discharged_cases<-as.integer(Naijacovid$Discharged_cases)
str(Naijacovid)
```

Next up, I want to create Additional columns for my Recovery Rate and  Death Rate

```{r}
Naijacovid$Recovery_rate<- (Naijacovid$Discharged_cases/Naijacovid$Confirmed_Cases)*100
Naijacovid$Death_rate<-(Naijacovid$No_of_Deaths/Naijacovid$Confirmed_Cases)*100
head(Naijacovid, 15)
```

Round up both recovery rate and death rate to 2 decimal places
```{r}
Naijacovid$Recovery_rate<- round(Naijacovid$Recovery_rate, 2)
Naijacovid$Death_rate<- round(Naijacovid$Death_rate, 2)
head(Naijacovid)
```
Check for missing data
```{r}
!complete.cases(Naijacovid)
```

Data is clean and Ready to roll.


```{r}
library(esquisse)
library(ggplot2)
```

Plots

```{r}
ggplot(Naijacovid) +
 aes(x = States_Affected, weight = Confirmed_Cases) +
 geom_bar(fill = "#0c4c8a") +
 labs(x = "States", y = "Total Number of Cases", title = "Total Confirmed Cases Vs States") +
 theme_dark()
```


